Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
Ajout des commentaires sur les img de comp

        When comparing the cluster detected to the cities that have more than $7\,000$ inhabitants, $3$-NN is the method that has the best result. In fact, if we consider all base station with a $\gamma_p$ value inferior to $\unit[2]{km}$ to be in cities we find that the percentage at accurately classified base station is $88\%$. It is $87\%$ for DBScan and $85\%$ for HDBScan.

>>>>

        When comparing the cluster detected to the cities that have more than $7\,000$ inhabitants, $3$-NN is the method that has the best result. In fact, if we consider all base station with a $\gamma_p$ value inferior to $\unit[2]{km}$ to be in cities we find that the percentage at accurately classified base station is $88\%$. It is $87\%$ for DBScan and $85\%$ for HDBScan. In Figure~\ref{fig:com_3NN},~\ref{fig:com_dbs} and~\ref{fig:com_hdb} those comparisons are illustrated: in red when the reference and the method agrees on city, in green on countryside and in blue when they don't agree.
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/city_det_comp/comp_3-NN.png}
            \caption{City detection comparison $3$-NN.}
            \label{fig:com_3NN}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/city_det_comp/comp_dbs.png}
            \caption{City detection comparison DBScan.}
            \label{fig:com_dbs}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/city_det_comp/comp_hdbs.png}
            \caption{City detection comparison HDBScan.}
            \label{fig:com_hdb}
        \end{figure}
